A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-06-29 tex/paper.tex
added flot submodule
Chebyshev arbitrary degree set by config
WASP run

@@

\comm{The following are some suggested paragraph outlines for a concise introduction:}

\comm{(1) start general: vast amount of information in an astronomical spectrum, and we want to 
make the most of that to learn about various physical parameters of interest.  accurate, unbiased 
stellar parameters (like temperature, gravity, metallicity, etc.) are of crucial importance in many 
astrophysics problems; e.g., exoplanets (and explain why), etc. (pick another one or two).}

\comm{(2) point out the challenge: quantitative extraction of these physical parameters is not 
easy.  go through some of the basic underlying limitations (practical, computational, limited 
models, etc.)}

\comm{(3) highlight various techniques/approaches being used (lots of references here).}

\comm{(4) now, without criticizing those approaches, just launch into a brief summary of our goals 
and a basic outline of the paper.}

\comm{I have made a lot of edits in Section 2, but have tried to restrict comments.  When there is 
something useful to say, I have added some commented-out text in the .tex file.}

@@

We can further divide $\vt_{\rm obs}$ into those parameters that impact the model primarily in the 
spectral or flux dimensions; $\vt_{\rm obs} = [\vt_{\rm obs, v}, \,\, \vt_{\rm obs, f}]$.  For the 
former, we consider three kernels that contribute to the observed line-of-sight velocity 
distribution function, $\varphi_v$.  The first, $\mathcal{F}_v^{\rm inst}$, treats the instrumental 
spectral broadening.  For illustrative purposes we assume $\mathcal{F}_v^{\rm inst}$ is a Gaussian 
with a mean at $v = 0$ and a constant width $\sigma_v$ at all $\lambda$, although more 
sophisticated forms could be adopted.  The second, $\mathcal{F}_v^{\rm rot}$, characterizes the 
broadening induced by (projected) stellar rotation, parameterized by $v\sin{i}$ as described by 
\citet[][his Eq.~18.14]{gray08}.  And the third, $\mathcal{F}_v^{\rm dop} = \delta(v-v_z)$, 
incorporates the radial velocity through a Doppler shift.  The model spectrum is modified by the 
parameters $\vt_{{\rm obs}, v} = [\sigma_v, \,\, v\sin{i}, \,\, v_z]$ through these kernels, using 
a convolution in velocity-space,
\begin{equation}
f_{\lambda}(\vt_{\ast}, \vt_{{\rm obs}, v}) = f_{\lambda}(\vt_{\ast}) \otimes \varphi_v = f_{\lambda}(\vt_{\ast}) \otimes \mathcal{F}_v^{\rm inst} \otimes \mathcal{F}_v^{\rm rot} \otimes \mathcal{F}_v^{\rm dop},
\label{eqn:broadening}
\end{equation}
and then re-sampled onto the discrete wavelengths corresponding to each data pixel, 
\begin{equation}
f_{\lambda}(\vt_{\ast}, \vt_{{\rm obs}, v}) \mapsto \vM(\vt_{\ast}, \vt_{{\rm obs}, v}),
\label{eqn:resampling}
\end{equation}
where the $\mapsto$ symbol denotes a re-sampling operator that maps the model spectrum onto the 
$N_{\rm pix}$-dimensional array $\vM$ (and $N_{\rm pix}$ is the number of pixels in the spectrum).  
For reference, Figure \ref{fig:broadening} shows a graphical representation of these 
post-processing steps.
% SA: My idea for this figure is sort of 1-column wide (~3.5"), with a set of spectral panels going 
% down vertically.  The top panel shows a segment of the full resolution model.  The next one down 
% can show the individual kernels described above, as well as their composite, \varphi_v.  Then the 
% next panel down can show the convolved (but still full-resolution) spectrum.  Finally, the bottom 
% panel will show the spectrum re-sampled onto the observed pixels.  It need not be a large figure 
% (maybe 5" long?).

@@

We adopt a somewhat analogous approach to deal with this issue, but cast it internal to the 
modeling framework to appropriately propagate the uncertainty introduced by additional degrees of 
freedom in the model.  The residual calibration errors are treated as an explicit contribution to 
the model spectrum, enabling us to explore the distribution of possible calibrations (see 
Section~\ref{subsec:MCMC}) and then eventually marginalize out the associated nuisance parameters.  
In essence, the inferences for the relevant stellar parameters will properly account for the 
underlying uncertainty in the calibration process.  This is achieved in practice by distorting the 
model spectrum with a (low-order) Chebyshev polynomial \citep[e.g.,][]{eisenstein+06,koleva09}, 
\begin{equation}
\vM(\vt, \vT_{\rm cheb}) = \vM(\vt) \times \sum_n c_n \, T_n,
\end{equation}
where $T_n$ are the standard Chebyshev functions of order $n$ and the coefficients are treated as a
set of nuisance (hyper-)parameters, $\vT_{\rm cheb} = \{c_n\}^{\rm order}$, for each available 
spectral order in the dataset.  With judicious priors on $\vT_{\rm cheb}$, we can ensure that the 
unintended treatment of real spectral features (e.g., broad, deep molecular bands) as calibration 
artifacts is negligible (see Secton~\ref{sec:examples} for examples).  The lowest-order (scaling) 
coefficient, $c_0$, is by its nature degenerate with the solid angle parameter, $\Omega$.  
Therefore, we enforce an additional constraint by requiring that the mean of the polynomial is 
unity.  For data with a single spectral order, this means setting $c_0 = 1$.  If the goal is to 
model multiple spectral orders, we assign $c_0 = 1$ in an arbitrary order as an anchor, but permit 
the $c_0$ values in other orders to be different (as necessary).  It is worth noting that this 
formalism can, in principle, be extended to develop models for completely uncalibrated spectra, 
rather than the residual calibration mismatches as described here (with a suitable relaxation of 
the priors on $\vT_{\rm cheb}$).  Figure \ref{fig:cheb} offers a practical demonstration of how 
these nuisance parameters are applied. 
% SA: I envision this figure much like the previous one, in a 1-column vertical distribution of 
% panels.  At top, you would show the data spectrum at an overlap of two spectral orders, along 
% with the post-processed model with no Chebyshev polynomials applied.  Next, you would show the 
% two Chebyshev polynomials appropriate for the two orders.  And then in the final panel you would 
% revisit the top panel with the polynomials applied, demonstrating the improvement.

@@

%\begin{figure*}[!htb]
%\begin{center}
%  \includegraphics{figs/badlines.pdf}
%  \caption{A collection of spectral lines which have imperfect model fits.
%    From left to right: \textbf{Class 0} The majority of spectral lines
%    ($\gtrsim 60$\%) will have minor differences in strength between data and
%    model spectrum, which produce low-amplitude correlations in the residuals
%    on the length scale of the width of a typical spectral line.  \textbf{Class
%    I}: Sometimes ($\lesssim 5$\% of all lines), a missing opacity source in
%    the model (in this case a line-blended \ion{Ca}{2}) leaves a large, highly correlated
%    patch of negative residuals.  \textbf{Class II}: Sometimes ($\lesssim 5$\%
%    of all lines), an extraneous line in the model leaves a large, highly
%    correlated patch of positive residuals.  \textbf{Class III}: If the line strengths are
%    substantially discrepant ($\lesssim 10$\% of all lines), there will be many
%    correlated residuals of moderate amplitude.  The difficulty
%    with class III lines is that for any specific line, there might exist a
%    $\vtstar$ that will fit the line, but there does not exist a $\vtstar$ that
%    will properly fit \emph{all} the lines.}
%\label{fig:badlines}
%\end{center}
%\end{figure*}

@@

Astronomical spectrographs are designed so that the detector over-samples the instrumental line 
broadening function with at least a few pixels.  Therefore, adjacent pixels are never completely 
independent samples of the observed spectrum.  In that case, a difference between an observed and 
modeled spectral feature will create a residual that spans multiple pixels.  This can be 
demonstrated in practice by examining the autocorrelation of the residual spectrum: a slight model 
mismatch will produce correlated residuals over a characteristic scale similar to the observational 
line-broadening kernel width.  Figure \ref{fig:class0} highlights a specific example of these 
correlated residuals in real data, where an imperfect model generates residuals which exhibit a 
significant autocorrelation signal on the scale of $\sim$4 pixels, which corresponds to the typical 
line width in this spectrum.  
% SA: It may be true that the figure you've made to demonstrate this is accurate, but it certainly 
% does not seem obvious to me what is going on in it.  I like the idea of the figure, but I think 
% it would be better demonstrated on a relatively smooth (continuum) region with a small spectral 
% mismatch, rather than deep lines everywhere.  Can we do that instead?

%\begin{figure*}[!htb]
%\begin{center}
%  $\vcenter{\hbox{\includegraphics{figs/class0_residuals.pdf}}}$
%  $\vcenter{\hbox{\includegraphics{figs/class0_autocorrelation.pdf}}}$
%  \caption{\textbf{Left} The same residuals from Figure~\ref{fig:badlines}, panel 0, but enlarged to show the mildly covariant structure produced by slight mismatch between the data and model spectra.   
%  \textbf{Right} The autocorrelation (Equation~\ref{eqn:autocorrelation}) of the residual sequence shown at left. Notice that there is significant correlation for offsets of $\lesssim 4$ pixels.}
%\label{fig:class0}
%\end{center}
%\end{figure*}

@@

%\begin{figure*}[!htb]
%\begin{center}
%\includegraphics[width=0.4\textwidth]{figs/matern_matrix.pdf}
%\includegraphics[width=0.4\textwidth]{figs/matern_draw.pdf}
%\caption{\textbf{Left} Inset zoomed to show a small region of a typical covariance matrix, generated using the kernel in Equation~\ref{eqn:global} and common values for the hyperparameters. There is a small degree of covariance in elements within a few pixels off the diagonal, which quickly tapers off so that the majority of the matrix remains sparse ($\sigma_{ij} = 0$). This matrix is used to model a spectrum which is correlated on a $\sim$few pixel scale.
%\textbf{Right} To demonstrate that this matrix properly models the correlated structure of the residuals, we compare the residuals to random residuals generated from a multivariate normal distribution with this covariance matrix. The top panel shows the same residuals shown in Figure~\ref{fig:class0}, and below are plotted three sets of simulated residuals. The amplitude and correlation length of the simulated residuals closely approximates the structure of the actual pixel residuals.}
%\label{fig:matern}
%\end{center}
%\end{figure*}

@@

Assuming that these local residuals are produced primarily by pathological differences in the 
spectral line strength (rather than shape or center), a simple Gaussian is a reasonable residual 
model.  In that case, the $k^{\rm th}$ such local residual can be described as
\begin{equation}
\vR_{\lambda}(a_k, \mu_k, \sigma_k) = \frac{a_k}{\sqrt{2\pi}{\sigma_k}} \exp \left[ - \frac{r^2(\lambda,\mu_k)}{2\sigma_k^2} \right],
\end{equation}
with an amplitude $a_k$, a mean wavelength $\mu_k$, and a width $\sigma_k$.  Following 
Eq.~\ref{eqn:expectation}, the kernel that describes the covariance of any two pixels related to 
the $k^{\rm th}$ residual region is
\begin{equation}
  \mathcal{K}_k(\lambda_i, \lambda_j | a_k, \mu_k, \sigma_k) = \frac{1}{2\pi} \left(\frac{a_k}{\sigma_k}\right)^2 \exp \left [ - \, \frac{r^2(\lambda_i, \mu_k) + r^2(\lambda_j, \mu_k)}{2 \sigma_k^2}\right ].
% SA: There was an error in this equation; the sigma in the denominator should be squared, but was 
%     not -- please check and make sure this is not manifested as a code bug.
\label{eqn:klocal}
\end{equation}
We again taper this kernel with a Hann window (Eq.~\ref{eqn:Hann}) to ensure computational 
efficiency with a sparse covariance matrix; in this case, the truncation distance $r_0$ can be set 
to some multiple of the Gaussian width (we set $r_0 = 4\sigma_k$).  
Figure \ref{fig:region} demonstrates how this non-stationary Gaussian 
kernel generates a localized region of enhanced variance that successfully mimics the kind of 
residuals produced by an inaccurate spectral line model.  In effect, these kernels down-weight the 
influence of such strong residuals in the likelihood calculation, mitigating any potential bias 
they might induce on inferences of the interesting parameters ($\vt$).  In essence, this is a 
robust, flexible, and unbiased method for (correlated) outlier rejection that preserves the 
integrity of the probabilistic framework being developed (as opposed to manual or threshold-based 
clipping/masking).  
% SA: The basic structure of this figure is nice.  But we should talk about making it presentation 
% quality once the other figures have been iterated as I've described (well, requested).

These local kernels can be further modified to account for more complex residual structures.  For 
example, late-type stars with imperfectly modeled molecular bandheads may produce a complicated 
pattern of positive and negative residuals or a pronounced mismatch over a relatively large 
spectral scale.  This phenomenologically different local covariance behavior can still be treated 
in this framework, if we permit the kernel in Eq.~\ref{eqn:klocal} to be modified by another 
(stationary) function.  Here we assume that function is a squared exponential,
\begin{equation}
  \mathcal{S}_k(\lambda_i, \lambda_j |\, h_k) = \exp \left ( - \, \frac{r_{ij}^2}{2\,h_k^2}\right ),
\end{equation}
where $h_k$ is a bandwidth parameter; small $h_k$ generates high-frequency structure, and vice 
versa.  The functionality of this kernel modification (where the appropriate kernel is now $w_k \, 
\mathcal{S}_k \, \mathcal{K}_k$) is demonstrated for the worked example presented in Section 
\ref{subsec:mdwarf}.  
% SA: I have to admit that I do not really understand this very well.  I think some appropriate 
% figures in Sect 3.2 will really help, though, so I'll wait for that before decided whether or not 
% we need to change this part of the text.

@@

We can now compute the covariance matrix employed in the likelihood calculation 
(Eq.~\ref{eqn:lnprob}) as the linear combination of these kernels and the trivial pixel-by-pixel 
noise matrix, 
\begin{eqnarray}
\vC_{ij}(\vT_{\rm cov}) & = & b \, \delta_{ij}\sigma_i + \\ \nonumber
         &   &  w(r_{ij}|r_0 = 4\ell) \,\, \mathcal{K}_g(\lambda_i, \lambda_j|a_g, \ell) + \\ \nonumber
         &   &  \sum_k w(r_{ij}|r_0 = 4\sigma_k) \,\, \mathcal{S}_k(\lambda_i,\lambda_j | h_k) \,\, \mathcal{K}_k(\lambda_i, \lambda_j | a_k, \mu_k, \sigma_k),
\end{eqnarray}
where the covariance hyperparameters $\vT_{\rm cov} = [a_g, \ell, \{a_k, \mu_k, \sigma_k, 
h_k\}^{N_{\rm reg}}]$, $N_{\rm reg}$ is the number of local residual regions (see below for 
details on how this is determined), and $b$ is assumed to be a fixed parameter that scales up the 
pixel noise values to account for interpolation uncertainties (see Section \ref{subsec:synthetic}; 
reasonable values are $b \approx 1.02$--1.10 for optical spectra; see Section \ref{sec:examples} 
for examples).

@@

%\begin{figure*}[!htb]
%\begin{center}
%\includegraphics[width=0.4\textwidth]{figs/gauss_matrix.pdf}
%\includegraphics[width=0.4\textwidth]{figs/gauss_draw.pdf}
%\caption{\textbf{Left} A typical covariance matrix including the Gaussian line kernel (Equation~\ref{eqn:line_total}). The same global covariance shown in Figure~\ref{fig:matern} is still present with the same hyperparameters, however now there is an additional patch of high covariance corresponding to the large, Gaussian-shaped residuals. These larger elements in the covariance matrix effectively down-weight the contribution of a poorly modeled synthetic spectral line.
%\textbf{Right} The same spectroscopic residuals shown in Figure~\ref{fig:badlines}, class I, shown with three random draws from the covariance matrix. The random draws can take on a range of amplitudes--positive, negative, or even flat--because they are simply random draws that are described by the covariance matrix. The wide range of possible residual amplitudes match the structure and amplitude of the pixel residuals.}
%\label{fig:region}
%\end{center}
%\end{figure*}

@@

%\todo{We can (should?) add an additional level to the hierarchy of
%  hyperparameters and add parameters to describe the \emph{population
%  characteristics} of poorly modeled spectral lines (mostly the typical width,
%  amplitude of these lines).  This will tell us about the frequency and
%distribution of spectral modelling errors.} 
%We explicitly fit for the hyperparemeters of the covariance kernels at the same
%time we fit for the stellar parameters. While including these extra
%parameters does increase the dimensionality and complexity of our model, they do provide several advantages. \emph{A priori} we do not know which
%regions of the spectrum are improperly modeled. The covariance hyperparameters provide a framework to identify these regions iteratively and in a self-consistent manner.

>>>>

\newcommand{\kms}{ \textrm{km s}^{-1} }

@@

A single stellar spectrum contains a vast amount of information about the physical properties of the star. It is of supreme interest to extract a maximal amount of this information from the spectrum in order to study the fundamental stellar parameters such as effective temperature, surface gravity, and metallicity. Accurate and unbiased estimates of stellar parameters are crucial to the study of numerous fields of astrophysics. For example, the mass, radius, and temperature of every newly discovered exoplanet (save for directly imaged planets) are measured relative to the properties of its host star. Large uncertainties or biases in the stellar parameters will translate into incorrect estimates of the habitable zone and the occurrence rate of earth-like planets \citep{kane14}. High quality stellar parameters are also necessary for the study of stellar evolution. Modelers of stellar evolution rely upon accurate samples of stellar parameters to chart the evolutionary tracks of stars through the Hertsprung-Russell diagram.

However, extracting physical parameters of stars from a stellar spectrum is often difficult, due to several factors. First, generating synthetic stellar spectra to use as a benchmark for comparison requires a sophisticated model of the stellar atmosphere and radiative transfer, along with an extensive, high-quality database of opacity sources. Accurately calibrating the atomic constants in this database is a laborious task, and requires high resolution, high signal-to noise spectra for verification, which limits targets mainly to extremely bright stars like the Sun and Vega. This makes it difficult to achieve the same precision when extending synthetic stellar models to intrinsically fainter stars, like M dwarfs, which have additional sources of molecular opacity. Second,  synthesizing a spectrum with such a sophisticated model requires a large amount of computational power, such that a full-optical spectrum at high resolution will take a day or more to process on a supercomputer.

Several, well-tested techniques exist that use spectra to infer stellar parameters. The most widely used technique relies upon measuring ratios of lines, or line indexes, which are matched to a set of indices measured from a synthetic spectrum. More sophisticated codes exist that synthesize spectra for direct comparison with certain well-studied lines, (e.g., \ion{Fe}{0}, \ion{Mg}{0}, and \ion{Ca}{0}) such as MOOG \citep{sneden73} and SME \citep{valenti96}. Other codes such as SPC \citep{buchhave12} cross-correlate the observed spectrum against a grid of pre-computed synthetic spectra and then fit a surface to the normalized cross-correlation coefficients to determine parameter uncertainties.

Owing to the high quality of libraries of pre-computed synthetic stellar spectra, it is now possible to generate an accurate forward model of a stellar spectrum. We seek to place this model in a Bayesian framework and construct a likelihood function suitable for comparing synthetic spectral models to real spectral data. We use a non-trivial covariance matrix, parameterized by a Gaussian process covariance kernel, to account for the residual pixel correlations that arise from a spectroscopic fit, which is a more complex problem than can be addressed with a simple $\chi^2$ best-fit metric. While designed for fitting stellar spectra, our method is general for all comparisons of spectra, and could be used to fit any type of spectra with a synthetic model, (e.g., galaxies or unresolved stellar clusters). In \S\ref{sec:method}, we describe the methodology, including a treatment of the covariance introduced by a spectroscopic fit. In \S\ref{sec:examples}, we present applications of our method to two examples, using optical spectra of an F type star and infrared spectra of an M star. In \S\ref{sec:discussion} we discuss the implications of our method and potential applications to develop data-driven models of stellar spectra.

@@

We can further divide $\vt_{\rm obs}$ into those parameters that impact the model primarily in the 
spectral or flux dimensions; $\vt_{\rm obs} = [\vt_{\rm obs, v}, \,\, \vt_{\rm obs, f}]$.  For the 
former, we consider three kernels that contribute to the observed line-of-sight velocity 
distribution function, $\varphi_v$.  The first, $\mathcal{F}_v^{\rm inst}$, treats the instrumental 
spectral broadening.  For illustrative purposes we assume $\mathcal{F}_v^{\rm inst}$ is a Gaussian 
with a mean at $v = 0$ and a constant width $\sigma_v$ at all $\lambda$, although more 
sophisticated forms could be adopted.  The second, $\mathcal{F}_v^{\rm rot}$, characterizes the 
broadening induced by (projected) stellar rotation, parameterized by $v\sin{i}$ as described by 
\citet[][his Eq.~18.14]{gray08}.  And the third, $\mathcal{F}_v^{\rm dop} = \delta(v-v_z)$, 
incorporates the radial velocity through a Doppler shift.  The model spectrum is modified by the 
parameters $\vt_{{\rm obs}, v} = [\sigma_v, \,\, v\sin{i}, \,\, v_z]$ through these kernels, using 
a convolution in velocity-space,
\begin{equation}
f_{\lambda}(\vt_{\ast}, \vt_{{\rm obs}, v}) = f_{\lambda}(\vt_{\ast}) \otimes \varphi_v = f_{\lambda}(\vt_{\ast}) \otimes \mathcal{F}_v^{\rm inst} \otimes \mathcal{F}_v^{\rm rot} \otimes \mathcal{F}_v^{\rm dop},
\label{eqn:broadening}
\end{equation}
and then re-sampled onto the discrete wavelengths corresponding to each data pixel, 
\begin{equation}
f_{\lambda}(\vt_{\ast}, \vt_{{\rm obs}, v}) \mapsto \vM(\vt_{\ast}, \vt_{{\rm obs}, v}),
\label{eqn:resampling}
\end{equation}
where the $\mapsto$ symbol denotes a re-sampling operator that maps the model spectrum onto the 
$N_{\rm pix}$-dimensional array $\vM$ (and $N_{\rm pix}$ is the number of pixels in the spectrum).  
For reference, Figure \ref{fig:broadening} shows a graphical representation of these 
post-processing steps.

\begin{figure*}[!htb]
\begin{center}
  \includegraphics{figs/kernels.pdf}
  \includegraphics{figs/high2low.pdf}
  \caption{Panel 1: the instrumental (${\rm FWHM} =6.8\;\kms$) and rotational ($v \sin i = 5\;\kms$) broadening kernels, and their composite. Panel 2: A section of the raw, high resolution synthetic model at $R=$500,000. Panel 3: The spectrum after applying the composite broadening kernel, $\varphi_v$. Panel 4: The broadened spectrum downsampled to the pixels of the detector.}
\label{fig:broadening}
\end{center}
\end{figure*}

% SA: My idea for this figure is sort of 1-column wide (~3.5"), with a set of spectral panels going 
% down vertically.  The top panel shows a segment of the full resolution model.  The next one down 
% can show the individual kernels described above, as well as their composite, \varphi_v.  Then the 
% next panel down can show the convolved (but still full-resolution) spectrum.  Finally, the bottom 
% panel will show the spectrum re-sampled onto the observed pixels.  It need not be a large figure 
% (maybe 5" long?).

@@

We adopt a somewhat analogous approach to deal with this issue, but cast it internal to the 
modeling framework to appropriately propagate the uncertainty introduced by additional degrees of 
freedom in the model.  The residual calibration errors are treated as an explicit contribution to 
the model spectrum, enabling us to explore the distribution of possible calibrations (see 
Section~\ref{subsec:MCMC}) and then eventually marginalize out the associated nuisance parameters.  
In essence, the inferences for the relevant stellar parameters will properly account for the 
underlying uncertainty in the calibration process.  This is achieved in practice by distorting the 
model spectrum with a (low-order) Chebyshev polynomial \citep[e.g.,][]{eisenstein06,koleva09}, 
\begin{equation}
\vM(\vt, \vT_{\rm cheb}) = \vM(\vt) \times \sum_n c_n \, T_n,
\end{equation}
where $T_n$ are the standard Chebyshev functions of order $n$ and the coefficients are treated as a
set of nuisance (hyper-)parameters, $\vT_{\rm cheb} = \{c_n\}^{\rm order}$, for each available 
spectral order in the dataset.  With judicious priors on $\vT_{\rm cheb}$, we can ensure that the 
unintended treatment of real spectral features (e.g., broad, deep molecular bands) as calibration 
artifacts is negligible (see Secton~\ref{sec:examples} for examples).  The lowest-order (scaling) 
coefficient, $c_0$, is by its nature degenerate with the solid angle parameter, $\Omega$.  
Therefore, we enforce an additional constraint by requiring that the mean of the polynomial is 
unity.  For data with a single spectral order, this means setting $c_0 = 1$.  If the goal is to 
model multiple spectral orders, we assign $c_0 = 1$ in an arbitrary order as an anchor, but permit 
the $c_0$ values in other orders to be different (as necessary).  It is worth noting that this 
formalism can, in principle, be extended to develop models for completely uncalibrated spectra, 
rather than the residual calibration mismatches as described here (with a suitable relaxation of 
the priors on $\vT_{\rm cheb}$).  Figure \ref{fig:cheb} offers a practical demonstration of how 
these nuisance parameters are applied. 
\comm{I envision this figure much like the previous one, in a 1-column vertical distribution of 
 panels.  At top, you would show the data spectrum at an overlap of two spectral orders, along 
 with the post-processed model with no Chebyshev polynomials applied.  Next, you would show the 
 two Chebyshev polynomials appropriate for the two orders.  And then in the final panel you would 
 revisit the top panel with the polynomials applied, demonstrating the improvement.}

@@

\begin{figure*}[!htb]
\begin{center}
  \includegraphics{figs/badlines.pdf}
  \caption{A collection of spectral lines which have imperfect model fits.
    From left to right: \textbf{Class 0} The majority of spectral lines
    ($\gtrsim 60$\%) will have minor differences in strength between data and
    model spectrum, which produce low-amplitude correlations in the residuals
    on the length scale of the width of a typical spectral line.  \textbf{Class
    I}: Sometimes ($\lesssim 5$\% of all lines), a missing opacity source in
    the model (in this case a line-blended \ion{Ca}{2}) leaves a large, highly correlated
    patch of negative residuals.  \textbf{Class II}: Sometimes ($\lesssim 5$\%
    of all lines), an extraneous line in the model leaves a large, highly
    correlated patch of positive residuals.  \textbf{Class III}: If the line strengths are
    substantially discrepant ($\lesssim 10$\% of all lines), there will be many
    correlated residuals of moderate amplitude.  The difficulty
    with class III lines is that for any specific line, there might exist a
    $\vtstar$ that will fit the line, but there does not exist a $\vtstar$ that
    will properly fit \emph{all} the lines.}
\label{fig:badlines}
\end{center}
\end{figure*}

@@

Astronomical spectrographs are designed so that the detector over-samples the instrumental line 
broadening function with at least a few pixels.  Therefore, adjacent pixels are never completely 
independent samples of the observed spectrum.  In that case, a difference between an observed and 
modeled spectral feature will create a residual that spans multiple pixels.  This can be 
demonstrated in practice by examining the autocorrelation of the residual spectrum: a slight model 
mismatch will produce correlated residuals over a characteristic scale similar to the observational 
line-broadening kernel width.  Figure \ref{fig:class0} highlights a specific example of these 
correlated residuals in real data, where an imperfect model generates residuals which exhibit a 
significant autocorrelation signal on the scale of $\sim$4 pixels, which corresponds to the typical 
line width in this spectrum.

\begin{figure*}[!htb]
\begin{center}
  $\vcenter{\hbox{\includegraphics{figs/class0_residuals.pdf}}}$
  $\vcenter{\hbox{\includegraphics{figs/class0_autocorrelation.pdf}}}$
  \caption{\textbf{Left} The same low-amplitude, mildly covariant residuals from Figure~\ref{fig:badlines}, panel 0, but enlarged to show the mildly covariant structure produced by slight mismatch between the data and model spectra.   
  \textbf{Right} The autocorrelation (Equation~\ref{eqn:autocorrelation}) of the residual sequence shown at left. Notice that there is significant correlation for offsets of $\lesssim 4$ pixels.}
\label{fig:class0}
\end{center}
\end{figure*}

@@

\begin{figure*}[!htb]
\begin{center}
\includegraphics[width=0.4\textwidth]{figs/matern_matrix.pdf}
\includegraphics[width=0.4\textwidth]{figs/matern_draw.pdf}
\caption{\textbf{Left} Inset zoomed to show a small region of a typical covariance matrix, generated using the kernel in Equation~\ref{eqn:global} and common values for the hyperparameters. There is a small degree of covariance in elements within a few pixels off the diagonal, which quickly tapers off so that the majority of the matrix remains sparse ($\sigma_{ij} = 0$). This matrix is used to model a spectrum which is correlated on a $\sim$few pixel scale.
\textbf{Right} To demonstrate that this matrix properly models the correlated structure of the residuals, we compare the residuals to random residuals generated from a multivariate normal distribution with this covariance matrix. The top panel shows the same residuals shown in Figure~\ref{fig:class0}, and below are plotted three sets of simulated residuals. The amplitude and correlation length of the simulated residuals closely approximates the structure of the actual pixel residuals.}
\label{fig:matern}
\end{center}
\end{figure*}

@@

Assuming that these local residuals are produced primarily by pathological differences in the 
spectral line strength (rather than shape or center), a simple Gaussian is a reasonable residual 
model.  In that case, the $k^{\rm th}$ such local residual can be described as
\begin{equation}
\vR_{\lambda}(a_k, \mu_k, \sigma_k) = \frac{a_k}{\sqrt{2\pi}{\sigma_k}} \exp \left[ - \frac{r^2(\lambda,\mu_k)}{2\sigma_k^2} \right],
\end{equation}
with an amplitude $a_k$, a mean wavelength $\mu_k$, and a width $\sigma_k$.  Following 
Eq.~\ref{eqn:expectation}, the kernel that describes the covariance of any two pixels related to 
the $k^{\rm th}$ residual region is
\begin{equation}
  \mathcal{K}_k(\lambda_i, \lambda_j | a_k, \mu_k, \sigma_k) = \frac{1}{2\pi} \left(\frac{a_k}{\sigma_k}\right)^2 \exp \left [ - \, \frac{r^2(\lambda_i, \mu_k) + r^2(\lambda_j, \mu_k)}{2 \sigma_k^2}\right ].
\label{eqn:klocal}
\end{equation}
We again taper this kernel with a Hann window (Eq.~\ref{eqn:Hann}) to ensure computational 
efficiency with a sparse covariance matrix; in this case, the truncation distance $r_0$ can be set 
to some multiple of the Gaussian width (we set $r_0 = 4\sigma_k$).  
Figure \ref{fig:region} demonstrates how this non-stationary Gaussian 
kernel generates a localized region of enhanced variance that successfully mimics the kind of 
residuals produced by an inaccurate spectral line model.  In effect, these kernels down-weight the 
influence of such strong residuals in the likelihood calculation, mitigating any potential bias 
they might induce on inferences of the interesting parameters ($\vt$).  In essence, this is a 
robust, flexible, and unbiased method for (correlated) outlier rejection that preserves the 
integrity of the probabilistic framework being developed (as opposed to manual or threshold-based 
clipping/masking).

These local kernels can be further modified to account for more complex residual structures.  For 
example, late-type stars with imperfectly modeled molecular bandheads may produce a complicated 
pattern of positive and negative residuals or a pronounced mismatch over a relatively large 
spectral scale.  This phenomenologically different local covariance behavior can still be treated 
in this framework, if we permit the kernel in Eq.~\ref{eqn:klocal} to be modified by another 
(stationary) function.  Here we assume that function is a squared exponential,
\begin{equation}
  \mathcal{S}_k(\lambda_i, \lambda_j |\, h_k) = \exp \left ( - \, \frac{r_{ij}^2}{2\,h_k^2}\right ),
\end{equation}
where $h_k$ is a bandwidth parameter; small $h_k$ generates high-frequency structure, and vice 
versa.  The functionality of this kernel modification (where the appropriate kernel is now $w_k \, 
\mathcal{S}_k \, \mathcal{K}_k$) is demonstrated for the worked example presented in Section 
\ref{subsec:mdwarf}.  
\comm{I have to admit that I do not really understand this very well.  I think some appropriate 
figures in Sect 3.2 will really help, though, so I'll wait for that before decided whether or not 
we need to change this part of the text.}

@@

We can now compute the covariance matrix employed in the likelihood calculation 
(Eq.~\ref{eqn:lnprob}) as the linear combination of these kernels and the trivial pixel-by-pixel 
noise matrix, 
\begin{eqnarray}
\vC_{ij}(\vT_{\rm cov}) & = & b \, \delta_{ij}\sigma_i + \\ \nonumber
         &   &  w(r_{ij}|r_0 = 4\ell) \,\, \mathcal{K}_g(\lambda_i, \lambda_j|a_g, \ell) + \\ \nonumber
         &   &  \sum_k w(r_{ij}|r_0 = 4\sigma_k) \,\, \mathcal{S}_k(\lambda_i,\lambda_j | h_k) \,\, \mathcal{K}_k(\lambda_i, \lambda_j | a_k, \mu_k, \sigma_k),
\end{eqnarray}
where the covariance hyperparameters $\vT_{\rm cov} = [a_g, \ell, \{a_k, \mu_k, \sigma_k, 
h_k\}^{N_{\rm reg}}]$, $N_{\rm reg}$ is the number of local residual regions
(see below for details on how this is determined), and $b$ is assumed to be a
fixed parameter that scales up the pixel noise values to account for read
noise, noise added during the 2D to 1D spectral extraction procedure, and
interpolation uncertainties (see Section \ref{subsec:synthetic}; reasonable
values are $b \approx 1.02$--1.10 for well-calibrated optical spectra; see Section
\ref{sec:examples} for examples).

@@

\begin{figure*}[!htb]
\begin{center}
\includegraphics[width=0.4\textwidth]{figs/gauss_matrix.pdf}
\includegraphics[width=0.4\textwidth]{figs/gauss_draw.pdf}
\caption{\textbf{Left} A typical covariance matrix including the Gaussian line kernel (Equation~\ref{eqn:line_total}). The same global covariance shown in Figure~\ref{fig:matern} is still present with the same hyperparameters, however now there is an additional patch of high covariance corresponding to the large, Gaussian-shaped residuals. These larger elements in the covariance matrix effectively down-weight the contribution of a poorly modeled synthetic spectral line.
\textbf{Right} The same spectroscopic residuals shown in Figure~\ref{fig:badlines}, class I, shown with three random draws from the covariance matrix. The random draws can take on a range of amplitudes--positive, negative, or even flat--because they are simply random draws that are described by the covariance matrix. The wide range of possible residual amplitudes match the structure and amplitude of the pixel residuals.}
\label{fig:region}
\end{center}
\end{figure*}

@@

\todo{We can (should?) add an additional level to the hierarchy of
  hyperparameters and add parameters to describe the \emph{population
  characteristics} of poorly modeled spectral lines (mostly the typical width,
  amplitude of these lines).  This will tell us about the frequency and
distribution of spectral modelling errors.} 
We explicitly fit for the hyperparameters of the covariance kernels at the same
time we fit for the stellar parameters. While including these extra
parameters does increase the dimensionality and complexity of our model, they do provide several advantages. \emph{A priori} we do not know which
regions of the spectrum are improperly modeled. The covariance hyperparameters provide a framework to identify these regions iteratively and in a self-consistent manner.

The traditional practice method of dealing with spectral mismatch is to simply mask out the regions of the spectrum which do not agree to within a certain tolerance.  Rather than arbitrarily excluding regions of the spectrum from the fit, these regions should instead be incorporated into in the fit with the appropriate weight. A model that includes covariance is far more likely than forcing the synthetic spectrum to fit perfectly, and far more flexible than arbitrarily masking regions which do not fit. The fitting procedure allows these weights to be determined self-consistently, such that lines which are slightly wrong can still bring information to bear on the stellar parameters. In fact, it may be the case that the lines that are off by a small amount (class 0 and III lines in Figure~\ref{fig:badlines}) actually provide the \emph{most information} about the stellar parameters, precisely because these lines are the most sensitive to stellar structure and consequentially are the most difficult to model correctly.
